The pollination trade-off

### 2018-03-01 publication/questions_observations_todo.Rmd
Double spacing

---
title: "The pollination trade-off"
subtitle: "Questions & Observations"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
date: "3/1/2018"
output: 
  bookdown::pdf_document2: 
    keep_tex: no
    number_sections: false
toc: false
---

>>>>

---
title: "The pollination trade-off"
subtitle: "Questions & Observations"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
date: "3/1/2018"
output: 
  bookdown::pdf_document2: 
    keep_tex: no
    number_sections: false
toc: false
header-includes:
  - \usepackage{setspace}
---

\onehalfspacing
